Investigation on GIT

### 2010-04-25 paper.tex
escribi un poquito de la intro

\confplacedate{Buenos Aires, Argentina, April 18, 2010}

@@

\PARstart Vamos a contar cuando surgió esta tecnología y sus principales 
exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 
similitudes con otros sistemas de versionado distribuidos como Mercurial. 
Un poco se contará las diferencias fundamentales entre las herramientas de 
versionado centralizadas y distribuidas, simplemente nombrando las diferencias 
pero no explicándolas.

>>>>

%\confplacedate{Buenos Aires, Argentina, April 18, 2010}

@@

\PARstart

%It is given that, in these times, modern software projects need a tool to 
%automatically track changes made in the source files, called Version Control Systems (VCS).

Version Control Systems (VCS) usually track the whole history of the
source code in a central server that everyone that can access. This 
central server contains all the changes and branches of the code and 
the users that can read the versions or commit changes have to connect 
to this repository.
Distributed Version Control Systems (DVCS) are a modern way of managing
revisions of software that do not have a centralized server, for this reason 
they are also called De-centralized Version Control Systems. Everybody has a 
copy of the full repository with all changes made in the history.

Vamos a contar cuando surgió esta tecnología y sus principales 
exponentes en la actualidad. Vamos a basarnos en GIT pero hay muchas 
similitudes con otros sistemas de versionado distribuidos como Mercurial. 
Un poco se contará las diferencias fundamentales entre las herramientas de 
versionado centralizadas y distribuidas, simplemente nombrando las diferencias 
pero no explicándolas.
